---
title: 'targets-rgee-extract'
output: 
  github_document:
    toc: TRUE
---


# targets-rgee-extract

```{r include=FALSE}
knitr::opts_knit$set(
	fig.path = 'man/figures'
)

library(targets)
library(sf)
```


### Sample image with polygons

For example, extract the maximum elevation in each polygon ("elevation"):

```{r}
tar_load(sample_image_with_polys)
head(sample_image_with_polys)
plot(sample_image_with_polys)
```



### Sample image with points

For example, extract the leading tree species at each point ("b1"):

```{r}
tar_load(sample_image_with_points)
head(sample_image_with_points)
plot(sample_image_with_points['b1'])
```



### Sample image collections with polygons

For example, extract the monthly water detection within polygons (2 = water, 1 = land)

```{r}
tar_load(sample_image_collection_with_polygons)
head(sample_image_collection_with_polygons)
plot(sample_image_collection_with_polygons)
```



### Sample image collections with points

For example, Landsat 8 bands at each point: 

```{r}
tar_load(sample_image_collection_with_points)
head(sample_image_collection_with_points)
plot(sample_image_collection_with_points)
```

Note - these are spread wide, where each measure is a new column. That
means they will likely need to be restructured for further processing. 



## Setup

System dependencies:

- gcloud (https://cloud.google.com/sdk/docs/install)
- python >= 3.5
- earthengine python package


First time using this project:

```{r, eval = FALSE}
Sys.setenv(DOWNLOAD_STATIC_LIBV8 = 1)
install.packages('renv')
renv::restore()
rgee::ee_Authenticate()
rgee::ee_Initialize(drive = TRUE)
```



### Dependencies

System dependencies above. 

Details for `rgee` here: https://r-spatial.github.io/rgee/articles/rgee01.html#installation



#### `rgee` 

The "first time" section above should get you set up, but if you are starting from scratch: 


**Install**:

```{r, eval = FALSE}
library(rgee)
ee_install(py_env = 'rgee')
```


**Authenticate**:

```{r, eval = FALSE}
ee_Initialize()
```


**Check**:

```{r, eval = FALSE}
ee_check()
```


Renv + python:

```{r, eval = FALSE}
renv::use_python(reticulate::py_discover_config()$python)
renv::snapshot()
```
