---
output: github_document
---


# targets-rgee-extract

```{r include=FALSE}
library(targets)
library(sf)

a <- targets::tar_visnetwork(targets_only = TRUE)
```

```{r, echo = FALSE}
a
```



### Sample image with polygons

For example, extract the maximum elevation in each polygon ("elevation"):

```{r}
head(tar_read(sample_image_with_polys))
```


### Sample image with points

For example, extract the leading tree species at each point ("b1"):

```{r}
head(tar_read(sample_image_with_points))
```

<!-- 
### Sample image collections with polygons

### Sample image collections with points
-->

## Setup

First time using this project:

```{r, eval = FALSE}
Sys.setenv(DOWNLOAD_STATIC_LIBV8 = 1)
install.packages('renv')
renv::restore()
rgee::ee_Authenticate()
rgee::ee_Initialize(drive = TRUE)
```

### Dependencies

Details for `rgee` here: https://r-spatial.github.io/rgee/articles/rgee01.html#installation

#### System dependencies

- gcloud (https://cloud.google.com/sdk/docs/install)
- python >= 3.5
- earthengine python package


#### `rgee` 

The "first time" section above should get you set up, but if you are starting from scratch: 


**Install**:

```{r, eval = FALSE}
library(rgee)
ee_install(py_env = 'rgee')
```


**Authenticate**:

```{r, eval = FALSE}
ee_Initialize()
```


**Check**:

```{r, eval = FALSE}
ee_check()
```


Renv + python:

```{r, eval = FALSE}
renv::use_python(reticulate::py_discover_config()$python)
renv::snapshot()
```
